|

### 2021-02-22 appendix/appendix.Rmd
appendix changes

@@

Consider a strategic interaction between two healthcare workers and a government agency.\footnote{This model was inspired in @bolton2005contract. It is a particular version of their model, aimed at illustrate the effects of our treatment.} The agency hires healthcare workers to provide preventive healthcare. And the workers decide the amount of effort they will exert, conditional on the compensation scheme they receive.

@@

## Training Participation Balance
tabcov <- data.frame()

# Altruism
x = tapply(pretreat$Age, 
           pretreat$training,
           mean)
y = summary(aov(Age~training, 
                data = pretreat))
tab <- data.frame(Var = 'Age',
                  `NotTraining` = round(x[1],2),
                  `Training` = round(x[2],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Age
x = tapply(pretreat$Female, 
           pretreat$training,
           mean)
y = summary(aov(Female~training, data = pretreat))
tab <- data.frame(Var = 'Female',
                  `NotTraining` = round(x[1],2),
                  `Training` = round(x[2],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Religiosity
x = tapply(pretreat$HasVehicle, 
           pretreat$training,
           mean)
y = summary(aov(HasVehicle~training, data = pretreat))
tab <- data.frame(Var = 'Has Vehicle?',
                  `NotTraining` = round(x[1],2),
                  `Training` = round(x[2],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# N
x = round(tapply(rep(1, length(pretreat$training)), 
                 pretreat$training,
                 sum), digits = 0)
tab <- data.frame(Var = 'N',
                  `NotTraining` = round(x[1],2),
                  `Training` = round(x[2],2),
                  FVal = NA,
                  Pvalue = NA)
tabcov <- rbind(tabcov, tab)
row.names(tabcov) <- NULL
```

\begin{table}[!htbp] \centering
  \caption{Covariate Balance on Training}
  \label{appctabcovbalindv}
\begin{tabular}{@{\extracolsep{5pt}} lcccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
Variable & Not Training & Training & F-Statistic & P-Value \\
\hline \\[-1.8ex]
```{r, echo=FALSE, results='asis'}
for (i in 1:dim(tabcov)[1]) {
  cat(paste(paste(tabcov[i,], collapse = ' & '), 
        ' \\\\ ', sep = ''), '\n')
}
```
\hline\hline \\[-1.8ex] 
\end{tabular}
\end{table}

@@

## Participation Balance
tabcov <- data.frame()

# Altruism
x = tapply(pretreat$Age, 
           pretreat$participating,
           mean)
y = summary(aov(Age~participating, 
                data = pretreat))
tab <- data.frame(Var = 'Age',
                  `NotParticipating` = round(x[1],2),
                  `Participating` = round(x[2],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Age
x = tapply(pretreat$Female, 
           pretreat$participating,
           mean)
y = summary(aov(Female~participating, data = pretreat))
tab <- data.frame(Var = 'Female',
                  `NotParticipating` = round(x[1],2),
                  `Participating` = round(x[2],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Religiosity
x = tapply(pretreat$HasVehicle, 
           pretreat$participating,
           mean)
y = summary(aov(HasVehicle~participating, data = pretreat))
tab <- data.frame(Var = 'Has Vehicle?',
                  `NotParticipating` = round(x[1],2),
                  `Participating` = round(x[2],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# N
x = round(tapply(rep(1, length(pretreat$participating)), 
                 pretreat$participating,
                 sum), digits = 0)
tab <- data.frame(Var = 'N',
                  `NotParticipating` = round(x[1],2),
                  `Participating` = round(x[2],2),
                  FVal = NA,
                  Pvalue = NA)
tabcov <- rbind(tabcov, tab)
row.names(tabcov) <- NULL
```

\begin{table}[!htbp] \centering
  \caption{Covariate Balance on Participation}
  \label{appctabcovbalindv}
\begin{tabular}{@{\extracolsep{5pt}} lcccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
Variable & Not Participating & Participating & F-Statistic & P-Value \\
\hline \\[-1.8ex]
```{r, echo=FALSE, results='asis'}
for (i in 1:dim(tabcov)[1]) {
  cat(paste(paste(tabcov[i,], collapse = ' & '), 
        ' \\\\ ', sep = ''), '\n')
}
```
\hline\hline \\[-1.8ex] 
\end{tabular}
\end{table}

@@

\begin{table}[!htbp] \centering
  \caption{Covariate Balance on Individual Characteristics}
  \label{appctabcovbalindv}
\begin{tabular}{@{\extracolsep{5pt}} lccccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
Variable & Control & Individual & Collective & F-Statistic & P-Value \\
\hline \\[-1.8ex]
```{r, echo=FALSE, results='asis'}
for (i in 1:dim(tabcov)[1]) {
  cat(paste(paste(tabcov[i,], collapse = ' & '), 
        ' \\\\ ', sep = ''), '\n')
}
```
\hline\hline \\[-1.8ex] 
\end{tabular}
\end{table}

@@

```{r, echo = FALSE}
## Census Sectors characteristics
tabcov <- data.frame()

@@

```{r, echo=FALSE}
tabcov <- data.frame()
# Number of Houses
x = dfr2 %>%
  group_by(D1) %>%
  summarise(x = weighted.mean(NHouses, weightsD1))
x = x$x
x
y = summary(aov(NHouses~D1, data = dfr2, weights=dfr2$weightsD1))
tab <- data.frame(Var = 'Number of Houses',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Number of households
x = dfr2 %>%
  group_by(D1) %>%
  summarise(x = weighted.mean(NHouseholds, weightsD1))
x = x$x
y = summary(aov(NHouseholds~D1, data = dfr2, weights=dfr2$weightsD1))
tab <- data.frame(Var = 'Number of Households',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# AvgHouseholdSize
x = dfr2 %>%
  group_by(D1) %>%
  summarise(x = weighted.mean(AvgHouseholdSize, weightsD1))
x = x$x
y = summary(aov(AvgHouseholdSize~D1, data = dfr2, 
                weights=dfr2$weightsD1))
tab <- data.frame(Var = 'Avg. Household Size',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Avg. Income Households
x = dfr2 %>%
  group_by(D1) %>%
  summarise(x = weighted.mean(logAvgIncomeHousehold, weightsD1))
x = x$x
y = summary(aov(logAvgIncomeHousehold~D1, data = dfr2, 
                weights=dfr2$weightsD1))
tab <- data.frame(Var = 'Log Avg. Income',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Cases Before
x = dfr2 %>%
  group_by(D1) %>%
  summarise(x = weighted.mean(plac, weightsD1))
x = x$x
y = summary(aov(plac~D1, data = dfr2, weights=dfr2$weightsD1))
tab <- data.frame(Var = 'Cases Before Treatment',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)
row.names(tabcov) <- NULL
```

@@

```{r, echo = FALSE, results='asis'}
## Productivity outcome
mprod <- list()
mprod[[1]] <- lm(nHouse ~ D, data = prodfr)
mprod[[2]] <- lm(nHouseLessTwoMin ~ D, data = prodfr)
mprod[[3]] <- lm(nBreed ~ D, data = prodfr)
mprod[[4]] <- lm(nLarvae ~ D, data = prodfr)
stargazer(mprod[[1]], mprod[[2]],
          mprod[[3]], mprod[[4]],
          se = starprep(mprod[[1]], mprod[[2]],
                        mprod[[3]], mprod[[4]],
                        se_type = "HC1"),
          dep.var.labels = c('\\shortstack{Houses \\\\ Visited}', 
                             '\\shortstack{Houses Vis. in \\\\ Less than Two Min.}',
                             '\\shortstack{Breeding Sites \\\\ Terminated}',
                             '\\shortstack{Larvae \\\\ Terminated}'),
          keep.stat = c('ser', 'n'),
          keep = c('DIndividual', 'DCollective'),
          covariate.labels = c('Individual Bonus',
                               'Collective Bonus'),
          title = 'Field Productivity', header = FALSE)
```

@@

1. There is a 10.3\% effect on the full data model.
2. The other windows are not significant but the sign is consistent with lower disease incidence.
3. Comparing individual and collective, collective decreases by 2.9\%, but the result is not significant.

@@

>>>>

\pagebreak

@@

Consider a strategic interaction between two healthcare workers and a government agency.\footnote{This model was inspired in the @bolton2005contract and the @itoh1991incentives. It is a particular case of their model, aimed at illustrate the effects of our treatment.} The agency hires healthcare workers to provide preventive healthcare. And the workers decide the amount of effort they will exert, conditional on the compensation scheme they receive.

@@

```{r, echo = FALSE, cache=TRUE}
#####
## Balance
#####

## Training Participation Balance
tabcov <- data.frame()
x = tapply(pretreat$Age, 
           pretreat$training,
           mean)
y = summary(aov(Age~training, 
                data = pretreat))
tab <- data.frame(Var = 'Age',
                  `NotTraining` = round(x[1],2),
                  `Training` = round(x[2],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)
x = tapply(pretreat$Female, 
           pretreat$training,
           mean)
y = summary(aov(Female~training, data = pretreat))
tab <- data.frame(Var = 'Female',
                  `NotTraining` = round(x[1],2),
                  `Training` = round(x[2],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)
x = tapply(pretreat$HasVehicle, 
           pretreat$training,
           mean)
y = summary(aov(HasVehicle~training, data = pretreat))
tab <- data.frame(Var = 'Has Vehicle?',
                  `NotTraining` = round(x[1],2),
                  `Training` = round(x[2],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)
x = round(tapply(rep(1, length(pretreat$training)), 
                 pretreat$training,
                 sum), digits = 0)
tab <- data.frame(Var = 'N',
                  `NotTraining` = round(x[1],2),
                  `Training` = round(x[2],2),
                  FVal = NA,
                  Pvalue = NA)
tabcov <- rbind(tabcov, tab)
row.names(tabcov) <- NULL
```

\begin{table}[!htbp] \centering
  \caption{Covariate Balance on Training}
  \label{baltraining}
\begin{tabular}{@{\extracolsep{5pt}} lcccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
Variable & Not Training & Training & F-Statistic & P-Value \\
\hline \\[-1.8ex]
```{r, echo=FALSE, results='asis'}
for (i in 1:dim(tabcov)[1]) {
  cat(paste(paste(tabcov[i,], collapse = ' & '), 
        ' \\\\ ', sep = ''), '\n')
}
```
\hline\hline \\[-1.8ex] 
\end{tabular}
\end{table}

@@

```{r, echo = FALSE, cache=TRUE}
#####
## Balance
#####

## Participation Balance
tabcov <- data.frame()
x = tapply(pretreat$Age, 
           pretreat$participating,
           mean)
y = summary(aov(Age~participating, 
                data = pretreat))
tab <- data.frame(Var = 'Age',
                  `NotParticipating` = round(x[1],2),
                  `Participating` = round(x[2],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)
x = tapply(pretreat$Female, 
           pretreat$participating,
           mean)
y = summary(aov(Female~participating, data = pretreat))
tab <- data.frame(Var = 'Female',
                  `NotParticipating` = round(x[1],2),
                  `Participating` = round(x[2],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)
x = tapply(pretreat$HasVehicle, 
           pretreat$participating,
           mean)
y = summary(aov(HasVehicle~participating, data = pretreat))
tab <- data.frame(Var = 'Has Vehicle?',
                  `NotParticipating` = round(x[1],2),
                  `Participating` = round(x[2],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)
x = round(tapply(rep(1, length(pretreat$participating)), 
                 pretreat$participating,
                 sum), digits = 0)
tab <- data.frame(Var = 'N',
                  `NotParticipating` = round(x[1],2),
                  `Participating` = round(x[2],2),
                  FVal = NA,
                  Pvalue = NA)
tabcov <- rbind(tabcov, tab)
row.names(tabcov) <- NULL
```

\begin{table}[!htbp] \centering
  \caption{Covariate Balance on Participation}
  \label{balpart}
\begin{tabular}{@{\extracolsep{5pt}} lcccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
Variable & Not Participating & Participating & F-Statistic & P-Value \\
\hline \\[-1.8ex]
```{r, echo=FALSE, results='asis'}
for (i in 1:dim(tabcov)[1]) {
  cat(paste(paste(tabcov[i,], collapse = ' & '), 
        ' \\\\ ', sep = ''), '\n')
}
```
\hline\hline \\[-1.8ex] 
\end{tabular}
\end{table}

\pagebreak

@@

\begin{table}[!htbp] \centering
  \caption{Covariate Balance on Individual Characteristics}
  \label{balindvchar}
\begin{tabular}{@{\extracolsep{5pt}} lccccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
Variable & Control & Individual & Collective & F-Statistic & P-Value \\
\hline \\[-1.8ex]
```{r, echo=FALSE, results='asis'}
for (i in 1:dim(tabcov)[1]) {
  cat(paste(paste(tabcov[i,], collapse = ' & '), 
        ' \\\\ ', sep = ''), '\n')
}
```
\hline\hline \\[-1.8ex] 
\end{tabular}
\end{table}

@@

```{r, echo = FALSE, cache=TRUE}
## Census Sectors characteristics
tabcov <- data.frame()

@@

```{r, echo=FALSE, warning=FALSE, results='hide'}
tabcov <- data.frame()
# Number of Houses
x = dfr2 %>%
  group_by(D1) %>%
  summarise(x = weighted.mean(NHouses, weightsD1),
            .groups = 'drop')
x = x$x
x
y = summary(aov(NHouses~D1, data = dfr2, weights=dfr2$weightsD1))
tab <- data.frame(Var = 'Number of Houses',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Number of households
x = dfr2 %>%
  group_by(D1) %>%
  summarise(x = weighted.mean(NHouseholds, weightsD1),
            .groups = 'drop')
x = x$x
y = summary(aov(NHouseholds~D1, data = dfr2, weights=dfr2$weightsD1))
tab <- data.frame(Var = 'Number of Households',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# AvgHouseholdSize
x = dfr2 %>%
  group_by(D1) %>%
  summarise(x = weighted.mean(AvgHouseholdSize, weightsD1),
            .groups = 'drop')
x = x$x
y = summary(aov(AvgHouseholdSize~D1, data = dfr2, 
                weights=dfr2$weightsD1))
tab <- data.frame(Var = 'Avg. Household Size',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Avg. Income Households
x = dfr2 %>%
  group_by(D1) %>%
  summarise(x = weighted.mean(logAvgIncomeHousehold, weightsD1),
            .groups = 'drop')
x = x$x
y = summary(aov(logAvgIncomeHousehold~D1, data = dfr2, 
                weights=dfr2$weightsD1))
tab <- data.frame(Var = 'Log Avg. Income',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Cases Before
x = dfr2 %>%
  group_by(D1) %>%
  summarise(x = weighted.mean(plac, weightsD1),
            .groups = 'drop')
x = x$x
y = summary(aov(plac~D1, data = dfr2, weights=dfr2$weightsD1))
tab <- data.frame(Var = 'Cases Before Treatment',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)
row.names(tabcov) <- NULL
```

@@

```{r, echo = FALSE, results='asis'}
## Productivity outcome
mprod <- list()
mprod[[1]] <- lm(nHouse ~ D, data = prodfr)
mprod[[2]] <- lm(nHouseLessTwoMin ~ D, data = prodfr)
mprod[[3]] <- lm(nBreed ~ D, data = prodfr)
mprod[[4]] <- lm(nLarvae ~ D, data = prodfr)
stargazer(mprod[[1]], mprod[[2]],
          mprod[[3]], mprod[[4]],
          se = starprep(mprod[[1]], mprod[[2]],
                        mprod[[3]], mprod[[4]],
                        se_type = "HC1"),
          dep.var.labels = c('\\shortstack{Houses \\\\ Visited}', 
                             '\\shortstack{Houses Vis. in \\\\ Less than Two Min.}',
                             '\\shortstack{Breeding Sites \\\\ Terminated}',
                             '\\shortstack{Larvae \\\\ Terminated}'),
          keep.stat = c('ser', 'n'),
          keep = c('DIndividual', 'DCollective'),
          covariate.labels = c('Individual Bonus',
                               'Collective Bonus'),
          title = 'Field Productivity', header = FALSE,
          font.size = 'small')
```

@@

1. There is a 10.3\% effect on the full data model.
2. The other windows are not significant but the sign is consistent with lower disease incidence.

\pagebreak

@@

### Parcial Implementation and Possible Threats to the Identification

We had one substantial problem during the field, with the partial implementation of the territorial assignment in the control group. The coordinator of the control group base changed the territorial assignment because of pressure from the participants that had to work farther from the base. The coordinator assigned pair for the surroundings of the base. This problem may potentially threat the territorial comparability of the cases, but to ensure that this is not confounding our results, we used propensity-score matching to re-weight these areas. After the matching, the sectors seems comparable, and we are confident that the re-weight allows a comparable territorial assignment.
